---
title       :  Predict wine prices
subtitle    :  replace expert with statistics 
author      :  Eason
job         :  Analyst on keyboard
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Read data from wine.csv
```{r}
wine = read.csv("wine.csv")
```
Take a look at the data
```{r}
summary(wine)
```

--- .class #id 

## Fit multivariate regression model on wine price
```{r}
model = lm(Price ~ AGST + HarvestRain + WinterRain + Age, data=wine)
summary(model)[4]
```
Here you can see the most important factor amongst all is AGST, of which coefficienct is 0.607. Age, to our surprise, does not affect as much as AGST does.



--- .class #id 

## Test our regression model
```{r}
wineTest = read.csv("wine_test.csv")
predictTest = predict(model, newdata=wineTest)
```
Take a look at out-of-sample error
```{r}
sum((wineTest$Price - predictTest)^2)
```

Compare it with in-sample error
```{r}
sum(model$residuals^2)
```


--- .class #id 

## Conclusion
As you can see, the prediction is pretty impressive.
You want to buy great wine but being afraid of getting ripped off?




# Predict it!

--- .class #id 
